Ripple Consensus Review

### 2015-04-26 paper.tex
Fix UNL outcomes table formatting

\documentclass{article}
\usepackage{url}
\usepackage{mathtools}
\usepackage{tikz}
% \usepackage{multirow}
\usetikzlibrary{arrows,positioning}
\begin{document}
\title{Ripple Consensus Review}
\author{Peter Todd}
\date{FIXME}
\maketitle

@@

Let's assume the node operator does not know what UNL other nodes in the
economic majority have chosen to use. They do however know the default UNL
provided by Ripple Labs, and they have a reasonable belief that other node
operators also know that UNL and may also be using it. The node operator's goal
is to limit losses; the best case is their node stays in consensus with other
nodes. Second best is they suffer a denial of service attack causing their node
to stop processing some or all transactions. Worst case is their node accepts
transactions that other nodes do not, making possible double-spend attacks.
Figure \ref{fig:unl-choice-plot} shows the outcomes of various possible
decisions by them and other node operators, ranging from $100\%$ default UNL,
$50\%$ default UNL, and $10\%$ default UNL.

@@

\begin{table}
    \begin{tabular}{c|c|c|c|}
        ~ & \multicolumn{3}{c}{Majority UNL \%} \\
        % \multirow{3}{*}{You} & $100\%$ & $50\%$ & $10\%$ \\ \hline
        $100\%$ & Consensus & DoS & DoS \\ \hline
        $50\%$ & DoS & DoS & Doublespend \\ \hline
        $10\%$ & Doublespend & Doublespend & Doublespend \\
    \end{tabular}
\end{table}

>>>>

\documentclass{article}
\usepackage{url}
% \usepackage{showframe}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{multirow}
\usetikzlibrary{arrows,positioning}
\begin{document}
\title{Ripple Consensus Review}
\author{Peter Todd}
\date{FIXME}
\maketitle

@@

Let's assume the node operator does not know what UNL other nodes in the
economic majority have chosen to use. They do however know the default UNL
provided by Ripple Labs, and they have a reasonable belief that other node
operators also know that UNL and may also be using it. The node operator's goal
is to limit losses; the best case is their node stays in consensus with other
nodes. Second best is they suffer a denial of service attack causing their node
to stop processing some or all transactions. Worst case is their node accepts
transactions that other nodes do not, making possible double-spend attacks.
Table \ref{tbl:unl-outcomes} shows the outcomes of various possible
decisions by them and other node operators, ranging from $100\%$ default UNL,
$50\%$ default UNL, and $10\%$ default UNL.

@@

\begin{table}
    \centering

    \begin{tabular}{cc|c|c|c}
        \multicolumn{2}{c}{} & \multicolumn{3}{c}{Majority} \\
        \multicolumn{2}{c}{} & $100\%$ & $50\%$ & $10\%$ \\ \cline{3-5}
        \multirow{3}{*}{Local} & $100\%$ & Consensus & DoS & DoS \\ \cline{2-5}
        ~ & $50\%$ & DoS & DoS & Doublespend \\ \cline{2-5}
        ~ & $10\%$ & Doublespend & Doublespend & Doublespend \\
    \end{tabular}

    \caption{Worst-case outcomes of default UNL \% choices}
    \label{tbl:unl-outcomes}
\end{table}
